no interaction

### 2022-08-22 graphs_newt_snakes/no_interact.Rmd
i fixed the problem with naming and reknit the file for tall GA1. I also am beginning to look at the dat for the no interaction plots.

inter_data_long_mean <- gatinter(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)

@@

>>>>

inter_data_long_mean <- gather(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)

@@

file_name= "Snake_1.0e-08_0.005_Newt_1.0e-08_0.005_3"
#Snake_1.0e-08_0.005_Newt_1.0e-11_0.158_0

spegen=13001
#unique(inter_grid_tall_file$snake_newt_rep)
inter<-inter_inter_grid_tall_file[which(inter_inter_grid_tall_file$snake_newt_rep==file_name & inter_inter_grid_tall_file$generation==spegen),]

inter_data_long_mean <- gather(inter_mean, condition, measurement, newt_mean_pheno_0:snake_mean_pheno_99, factor_key=TRUE)
